Analyse von Common Crawl

### 2015-07-05 presentation/presentation.tex
Add extraction flowchart to presentation

@@

\subsection{Extraktion}
\begin{frame}{\insertsection: \insertsubsection}
\end{frame}

>>>>

\tikzstyle{block} = [rectangle, draw, text width=7em, text centered, rounded corners, minimum height=4em]
\tikzstyle{line} = [draw, -latex']

\subsection{Extraktion}
\begin{frame}{\insertsection: \insertsubsection}
    \centering
    \vspace{.5cm}
    \begin{tikzpicture}[auto]
        \node[block] (CC) at (0,0) {Common Crawl};
        \node[block, right=4cm of CC] (META) {meta-extractor\footnotemark};
        \node[block, below=2cm of META] (MONET) {MonetDB};
        \node[block, left=4cm of MONET] (R) {R};
        \path[line] (CC) -- node {Download (curl)} (META);
        \path[line] (META) -- node {csv} (MONET);
        \path[line] (MONET) -- node {MonetDB.R} (R);
    \end{tikzpicture}
    \footnotetext{\url{https://github.com/klemens/ALI-CC}}
\end{frame}

@@
